INSTRUCTIONS TO PREPARE A FULL PAPER FOR THE 9th EUROPEAN CONGRESS ON COMPUTATIONAL METHODS IN APPLIED SCIENCES AND ENGINEERING\break ECCOMAS CONGRESS 2024

### 2024-03-07 paper/paper.tex
update paper.pdf
crop unit cell png
add global domain png

>>>>

\subsection{Problem setup}

\begin{figure}
    \begin{center}
        \includegraphics[width=0.65\textwidth]{../figures/beam/unit_cell.png}
    \end{center}
    \caption{Unit cell domain partition.}\label{fig:unit_cell_domain}
\end{figure}

\begin{figure}
    \begin{center}
        \includegraphics[width=0.65\textwidth]{../figures/beam/global_domain.png}
    \end{center}
    \caption{The partition of the global domain. The colors indicate the variation in Young's modulus for each subdomain.}\label{fig:global_domain}
\end{figure}
